\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-06 AffineLieAlgebras/InformalNotes/article.tex
Affine A1 to B2 example is completed.

The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}. The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
Thus here we show the simplest possible example of reduction of affine $\widehat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.

The simple roots for the affine $\widehat{A_1}$ are
\begin{equation}
  \label{eq:2}
  (\alpha,\delta-\alpha)
\end{equation}
We consider the embedding with the root $\beta=\delta-\alpha$.

Positive roots of the $\widehat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
The set of the

@@

The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\widehat{A_1}$ is the same as in the finite-dimensional case.

Consider the level one representation of the algebra $\mathfrak{g}=\widehat{B_2}$ with the highest weight $(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

@@

\begin{figure}[ph]
  \centering
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\widehat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

\section{Physical applications}
\label{sec:phys-appl}
\begin{comment}
  Rewrite it in more scientific style or drop this section.
\end{comment}
Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models.

>>>>

The maximal embeddings of the finite-dimensional Lie algebras into the affine Lie algebras were thoroughly studied and the tables of the branching coefficients are given in the book \cite{kass1990ala}. The task of the study of non-maximal embeddings is then can be reduced to the well-known task of branching of the finite-dimensional Lie algebras.
Thus here we show the simplest possible example of reduction of affine $\hat{A_1}$ to $A_1$ in order to demonstrate some traits of our method and show that we eliminate the need of slice-by-slice study discussed in \cite{kass1990ala}.

The simple roots for the affine $\hat{A_1}$ are
\begin{equation}
  \label{eq:2}
  (\alpha,\delta-\alpha)
\end{equation}
We consider the embedding with the root $\beta=\delta-\alpha$.

Positive roots of the $\hat{A_1}$ are $\alpha,\; \alpha+n\delta,\; n\delta,\; -\alpha+n\delta;\; n=1,2,3,\dots$.
The set of the

@@

The set $\Delta_{\bot}$ of the orthogonal positive roots with the zero projection on the root space of the subalgebra $\hat{A_1}$ is the same as in the finite-dimensional case.

Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

@@

\begin{figure}[ph]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the figure
\begin{figure}[ph]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \includegraphics[width=150mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:B4B2Fan}
\end{figure}

Also we should mention that the lowest vector of the fan $\gamma_0$ is equal to zero, since we have excluded all the roots of $\Delta_{\bot}$ from the defining relation (\ref{fan-defined}).

Using the recurrent relation for the anomalous branching coefficients we get the following result
\begin{figure}[ph]
  \includegraphics[width=150mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
\section{Physical applications}
\label{sec:phys-appl}
\begin{comment}
  Rewrite it in more scientific style or drop this section.
\end{comment}
Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models.
